\null \vfill \noindent{\bf\Large
Acknowledgement}
\bigskip

\noindent 
This thesis would not be finished without the help and support of many people that are impossible to name in a single page, but I would like to, none-the-less, acknowledge several people that, I feel, mostly contributed to the work, presented in this document, and who deserve a big thanks. First and foremost I would like to thank Jaro and Jana Bielčíkovi for their continuing and unwavering support during the entire course of my studies. Be it with with life and professional advice, good leadership, motivation, and last but not least, financial support. My doctoral studies were some of the best years of my life and I cannot imagine that they would be the same without my two supervisors. Moreover, several calamities were avoided only thanks to Jaro Bielčík and his support for all of which he will have my gratitude for the rest of my life.

I would also like to thank my dear friends at Lawrence Berkeley National Laboratory, Xin Dong, Mustafa Mustafa, and Sooraj Radhakrishnan who helped jumpstarting my journey into science and programming with good advice and leadership by example. I will always aspire to uphold the work standards and integrity I have learnt at Berkeley.

Another big thanks goes to Zhangbu Xu and Les Bland from Brookhaven National Laboratory. Zhangbu Xu  helped me with the introduction into the works of the ZDC detector and STAR in general. Later, he also helped  me with support and good leadership, thanks to which the ZDC continued to work smoothly for all these years. Without the advice and supervision of Les Bland, the ZDC PMT test  and upgrade would not be possible and STAR functions in part thanks to him.

With regards to the text in this thesis, a big thanks goes to Filip Křížek from NPI CAS who helped with the corrections of several chapters. A lot of work went into these corrections and I appreciate it.

Lastly, I would like to thank all the STAR collaborators, several of whom I consider life-long friends and who made this journey such a blast.

\noindent\emph{Thank you all!}


\newpage \cleardoublepage
