In this thesis, the first direct reconstruction of $\Lambda_\mathrm{c}$ in Au+Au collisions at \snnFull\ is reported. Baryon to meson ratio in the charm sector has been measured in the form of \Lambdac/\dzero\@. 

The measurement of the \Lambdac\ in heavy-ion collisions represents a challenging task, due to the short life time ($c\tau \approx 60\,\upmu$m) and the large combinatorial background, because the direct reconstruction requires three body decays that involve pions, protons, and kaons which are abundant products of Au+Au collisions. The measurement was enabled thanks to the utilization of the new silicon detector HFT whose two innermost layers were placed very close to the interaction point and utilize the MAPS technology for the first time in heavy-ion experiments\@. Because of this, the innermost layers of the HFT have excellent granularity. Machine-learning techniques were utilized to separate the signal from the combinatorial background, which come mostly from the primary vertex. The relatively large sample of the \Lambdac, that was obtained thanks to these detection techniques, allowed for the \Lambdac/\dzero\ measurement to be differentiated in the transverse momentum and centrality for the first time in heavy-ion collisions.

The \Lambdac/\dzero\ yield ratio in Au+Au collisions at midrapidity ($|y| < 1$) is significantly larger than that in p+p collisions simulated by PYTHIA and is comparable with the baryon-to-meson ratios in the light- and strange-flavor hadrons in the same kinematic region. The measured ratio is also compatible with models that include charm-quark coalescence in the hadronization process.
The \Lambdac/\dzero\ ratio increases with more central collisions which is also consistent with models that include charm-quark coalescence.

The \pt-integrated \Lambdac/\dzero\ ratio was obtained by extrapolating the measurement to low \pt\ and is calculated as $0.80\pm0.12\text{(stat.)}\pm0.22\text{(sys., data)}\pm0.41\text{(sys., models extrapolation)}$\@. This shows that the \Lambdac\ make a sizable contribution to the total charm yield in heavy-ion collisions at RHIC. The \pt-integrated ratio is also consistent with the THERMUS model, in our comparison calculated with the thermal freeze-out temperature of $T_\mathrm{ch} = 160\,$MeV\@.


Two service tasks were performed as a part of this thesis: Work on the slow simulator for the HFT-Pixel detector and, secondly, maintenance, calibration, and documentation of the STAR Zero Degree Calorimeter (ZDC). 

The HFT recorded data at STAR the years 2014--2016 and was a critical upgrade for the precise measurements of open-charm hadrons, including enabling the measurement of the \Lambdac\@. The HFT-Pixel slow-simulator implementation and evaluation helped with the clustering component of the embedding procedure, in which simulated tracks are embedded into measured collisions at STAR\@. 

The ZDC plays a vital role for triggering and the assessment of instant luminosity at STAR, and the determination of centrality in ion--ion collisions. The task was to ensure smooth operation of this critical component during the data taking at STAR\@. The ZDC was calibrated, using the single-neutron peak, at the start of each run. The performance of the ZDC photo-multiplier tubes has been evaluated and several have been upgraded to ones with higher gain. Moreover, the entire setup of the ZDC, together with the control, trigger, and readout electronics have been documented~\cite{ZDCmanual}\@.



% an be improved by a better cut optimization and by using the 
% The statistical uncertainty cmixed-event method for the extraction of the combinatorial background. The systematic uncertainty needs a more thorough study of all the factors, contributing to it. Therefore, there is room for improvement of this result before publication. More observables are also being extracted from the data, including \Lambdac\ azimuthal anisotropy, and the ratio between the baryon $\Lambdac^+$ and the anti-baryon $\overline{\Lambdac}^-$ which has a potential to shed more light on the process of quark coalescence.
% 
% Moreover, STAR has recorded approximately twice more data in 2016, compared to the year 2014 with better performance of the HFT\@. This will allow to measure the ratio of $\Lambda_\mathrm{c}$ to D$^0$ in more centrality and $p_\mathrm{T}$ bins to put more constrain on theoretical predictions. 
